Inferring the gravitational potential of the Milky Way with a few precisely measured stars

### 2014-02-17 text/paper2/ms.tex
new figure
added figure

@@

In \paperone, we define a set of coordinates relative to the instantaneous phase-space position of the progenitor, $(\bs{r}_{p},\bs{v}_{p})$, normalized by the instantaneous tidal radius and escape velocity. Here we (1) instead scale the velocity coordinates by the velocity dispersion of the satellite, (2) reduce the dimensionality by considering only the magnitude of these vectors, and (3) take the logarithm of the magnitude,
\begin{equation}
  R = \ln\left(\frac{\left\vert\bs{r} - \bs{r}_{p}\right\vert}{R_{\rm tide}}\right)\,\,\,\,,\,\,\,\,
  V = \ln\left(\frac{\left\vert\bs{v} - \bs{v}_{p}\right\vert}{\sigma_v}\right).
\end{equation}
Figure~\ref{fig:reldists} shows distributions of $R$ and $V$ at $t=t_{\rm ub}$ for all particles as a function of progenitor mass from the simulations described in Section~\ref{sec:sims}. In these scaled coordinates, the distributions

- Point out constant $\sigma$ over mass\\
- Good until 2.5e9\\
- Proper description models 2D distribution, but [...]

%a phase-space distance, $D_{ps}$, as the sum of the normalized, relative position, $\frac{\bs{r}-\bs{r}_p}{\rtide}$, and velocity, $\frac{\bs{v}-\bs{v}_p}{v_{\rm esc}}$, for a stream star. We minimized the generalized variance of the 6D distribution over each normalized coordinate evaluated at the time that each star has minimum $D_ps$. This simple idea proved quite powerful for constraining properties of the LM10 potential used simulated observations of their N-body simulation. However, this method does not properly incorporate observational uncertainties.

\begin{figure}[h]
\begin{center}
% \includegraphics[width=\textwidth]{/Users/adrian/projects/streams/plots/paper2/rel_dists.pdf}
\caption{ TODO }\label{fig:reldist}
\end{center}
\end{figure}

%The core of this method provides a basis for the probabilistic model presented below.

>>>>

\begin{figure}[h]
\begin{center}
\includegraphics[width=\textwidth]{../../plots/paper2/simulated_streams.pdf}
\caption{ TODO }\label{fig:sims}
\end{center}
\end{figure}

@@

In \paperone, we define a set of coordinates relative to the instantaneous phase-space position of the progenitor, $(\bs{r}_{p},\bs{v}_{p})$, normalized by the instantaneous tidal radius and escape velocity. Here we (1) instead scale the velocity coordinates by the velocity dispersion of the satellite, (2) reduce the dimensionality by considering only the magnitude of these vectors, and (3) take the logarithm of the magnitude,
\begin{equation}
  R = \ln\left(\frac{\left\vert\bs{r} - \bs{r}_{p}\right\vert}{R_{\rm tide}}\right)\,\,\,\,,\,\,\,\,
  V = \ln\left(\frac{\left\vert\bs{v} - \bs{v}_{p}\right\vert}{\sigma_v}\right).
\end{equation}
Figure~\ref{fig:R_V} shows distributions of $R$ and $V$ --- computed at $t=t_{\rm ub}$ for each particle --- as a function of progenitor mass from the simulations described in Section~\ref{sec:sims}. In these scaled, log coordinates we model distributions in $R$ and $V$ as Gaussians. We find that for masses $\lesssim10^9M_\odot$, the variance ($\sigma^2$ in plot panels) remains approximately constant and the mean stays fixed at 0. For the largest mass simulation ($2.5\times10^9M_\odot$), the perturbation to the total potential due to the progenitor halo becomes significant and thus a large fraction of the stars are disrupted through interactions with the subhalo. For this article, we ignore covariances between $R$ and $V$. The

\begin{figure}[h]
\begin{center}
\includegraphics[width=\textwidth]{../../plots/paper2/R_V.pdf}
\caption{ TODO }\label{fig:R_V}
\end{center}
\end{figure}
